null_model

### 2020-09-23 analysis/calc_fd.Rmd
Eliminate plots that don't meet criteria at the get go when creating the master dataset (biotime_traits)

FD function:
```{r}
biotime_traits <- pins::pin_get("biotime-traits", board = "github")

get_fd <- function(obs_data, filter_plot, ...){
  require(FD)

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>% 
  filter(plot_id != "169A") %>% #soemthing strange going on with this one, a duplicate species obs in 2006
  ungroup() #%>%
  #filter(#!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327, 195)) #exclude to get the file size smaller

>>>>

FD function:
```{r}
get_fd <- function(obs_data, filter_plot, ...){
  require(FD)

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- pins::pin_get("biotime-traits", board = "github")

### 2020-09-23 analysis/ts_null_model.Rmd
Eliminate plots that don't meet criteria at the get go when creating the master dataset (biotime_traits)

#get the plots that meet our criteria for calculating FD
sample_plots <- biotime_traits %>%
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>%
  ungroup()

trait_data <- sample_plots %>% 
  select(-c(biotimeName, taxa, id_species, plot, year, weight, 
            traitName, scientificName, plot_id, study_id)) %>%
  distinct()

@@

Get sample dataframe
```{r}
future::plan(multiprocess)
sample_occurrence <- future_map(unique(sample_plots$plot_id), get_plot_sample, data = sample_plots, n = n) %>%
  bind_rows() %>%
  replace(is.na(.), 0)
```

>>>>

trait_data <- biotime_traits %>% 
  select(-c(biotimeName, taxa, id_species, plot, year, weight, 
            traitName, scientificName, plot_id, study_id)) %>%
  distinct()

@@

Get sample dataframe
```{r}
future::plan(multiprocess)
sample_occurrence <- future_map(unique(biotime_traits$plot_id), get_plot_sample, data = biotime_traits, n = n) %>%
  bind_rows() %>%
  replace(is.na(.), 0)
```
